submission

### 2024-03-09 submission.Rmd
added task describtion

@@

## 2.2 Calculating all p-values

@@

@@

```
## 2.4 Benjamini-Hochberg procedure

@@

##2.5 Holm–Bonferroni method

>>>>

**Task description:**: We first want to study the gene which is the most correlated with the level of cholesterol. Identify this gene and plot cholesterol as a function of this gene expression level. Fit a linear model. Test if there is a significant relation between this gene expression and cholesterol?

@@

## 2.2 Calculating all p-values
**Task description:**: We now wish to perform the previous test for all of the 3116 genes. For each of the genes, fit a linear model that explains cholesterol as a function of the gene expression and compute the p-value of the test.

@@

**Task description:**Order the p-values and plot the ordered as a function of their rank. On the same plot, display the line y=x/3116. Discuss the result.

@@

```
## 2.4 Benjamini-Hochberg procedure
**Task description:**Identify a set of genes linked to the response (aka discoveries). We want to guarantee that the expected proportion of false discoveries (mistakes) is less than 5%. Explain how you proceed and how many genes you discover.

@@

##2.5 Holm–Bonferroni method
**Task description:** We wish to be more conservative and guarantee that the probability of making a false discovery (or more) is less than 5%. Explain how you proceed and how many genes you discover.
